#I'm so sorry that here I use the new data to try dplyr. Because I want to keep the result, I also put this code on github. And the try of bridges data is in the downloadBridges.R

#Here is the data description of this dataset:http://archive.ics.uci.edu/ml/datasets/Communities+and+Crime+Unnormalized# 

#Data Import

```{r}
library(plyr)
library(choroplethr)
library(dplyr)
library(readr)
library(data.table)
dest="http://archive.ics.uci.edu/ml/machine-learning-databases/00211/CommViolPredUnnormalizedData.txt"
tmp=fread(dest,na.strings = '?')
tmp=as.tbl(tmp)
CC=tmp
page="http://archive.ics.uci.edu/ml/datasets/Communities+and+Crime+Unnormalized#"
lines=read_lines(page)
needed.lines=lines[566:712]
(variables.names=sub(pattern="<br>@attribute\\s(.*?)\\s(.*)",replacement="\\1",x=needed.lines))
variables.names=as.vector(variables.names)
names(CC)=variables.names
```

#Test NULL

```{r}
is.na(CC) %>% rowSums %>% hist(breaks=30)
is.na(CC) %>% colSums %>% hist
```


#Select needed variables

```{r}
needed=c("communityname","State","countyCode","communityCode","pop","perHoush","medIncome","medFamIncome","perCapInc","persPoverty","pctPoverty","pctAllDivorc","murdPerPop","rapesPerPop","robbbPerPop","assaultPerPop","burglPerPop","larcPerPop","autoTheftPerPop","arsonsPerPop","violentPerPop","nonViolPerPop")
needed.data=select(CC,one_of(needed))
```

#ggplot of total crime vs some variables I am interested in

```{r}
library(ggplot2)
ggplot(data=needed.data,mapping = aes(x=perHoush,y=murdPerPop+rapesPerPop+robbbPerPop+assaultPerPop+burglPerPop+larcPerPop+autoTheftPerPop+arsonsPerPop+violentPerPop+nonViolPerPop))+geom_point()+geom_smooth()
ggplot(data=needed.data,mapping = aes(x=medIncome,y=murdPerPop+rapesPerPop+robbbPerPop+assaultPerPop+burglPerPop+larcPerPop+autoTheftPerPop+arsonsPerPop+violentPerPop+nonViolPerPop))+geom_point()+geom_smooth()
ggplot(data=needed.data,mapping = aes(x=medFamIncome,y=murdPerPop+rapesPerPop+robbbPerPop+assaultPerPop+burglPerPop+larcPerPop+autoTheftPerPop+arsonsPerPop+violentPerPop+nonViolPerPop))+geom_point()+geom_smooth()
ggplot(data=needed.data,mapping = aes(x=perCapInc,y=murdPerPop+rapesPerPop+robbbPerPop+assaultPerPop+burglPerPop+larcPerPop+autoTheftPerPop+arsonsPerPop+violentPerPop+nonViolPerPop))+geom_point()+geom_smooth()
ggplot(data=needed.data,mapping = aes(x=pctPoverty,y=murdPerPop+rapesPerPop+robbbPerPop+assaultPerPop+burglPerPop+larcPerPop+autoTheftPerPop+arsonsPerPop+violentPerPop+nonViolPerPop))+geom_point()+geom_smooth()
ggplot(data=needed.data,mapping = aes(x=pctAllDivorc,y=murdPerPop+rapesPerPop+robbbPerPop+assaultPerPop+burglPerPop+larcPerPop+autoTheftPerPop+arsonsPerPop+violentPerPop+nonViolPerPop))+geom_point()+geom_smooth()
```

#Total crime per 100k population with wisconsin map

```{r}
library(choroplethrMaps)
wi=filter(needed.data,State=="WI")
wi = mutate(wi, fips = 55000+countyCode)
by_fips=group_by(wi,fips)
sumcrime=summarise(by_fips,sum(murdPerPop+rapesPerPop+robbbPerPop+assaultPerPop+burglPerPop+larcPerPop+autoTheftPerPop+arsonsPerPop+violentPerPop+nonViolPerPop))
sumcrime=data.frame(sumcrime)
sumcrime%>% transmute(region = fips, value = sumcrime[,2]) %>% county_choropleth(state_zoom = "wisconsin") #total crime

```


